TBD

### 2019-09-05 manuscript/manuscript.Rmd
added in evolvability results and adjusted methods. also tried to include some more biological reasoning for the patterns of selection.

---
# Decided to manually format the title page because I had greater control. Note that you should use put this info in the YAML header for compatability across document formats (e.g. html)
#title: Phenotypic evolution is more constrained in simpler food webs
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$ 
#- Christopher J. Greyson-Gaito$^{2,3}$ 
#- Arezoo Sootodeh$^{2}$ 
#- Brendan Locke$^{4}$ 
#- Jordi Bascompte$^{1}$ 
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: eco_let
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

*Manuscript type*: Article. <!-- Or e-article, note, e-note, natural history miscellany, e-natural history miscellany, comment, reply, invited symposium, or countdown to 150.-->

@@

\footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize

@@

The loss of biodiversity is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways. For example, in a <!--multitrophic community or -->food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection. Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities. To examine these different possibilities, we conducted a field experiment that simulated the extinction of a consumer guild associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig. \ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006]. These galls protect larva from attack by generalist predators (e.g. ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016]. We manipulated food-web structure by either excluding the guild of larval parasitoids (extinction food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (original food web, fig. \ref{fig:Conceptual}). The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system. While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene. Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid. We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape. Taken together, our study gives insight to how the loss of biodiversity may constrain the evolution of interacting populations.

@@

Our analysis consisted of three parts. First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment. Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients. Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we used to measure evolutionary constraints.

@@

$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination. In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait. Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence). Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix. For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature matrix in each food-web treatment. This provides a conservative estimate of the factors contributing to the curvature of the adaptive landscape.

Note that our metrics of selective and genetic constraints do not put much stock in differences in the magnitude of selection between food-web treatments. This is because there is a high likelihood that we are underestimating the magnitude of selection in our treatment that excludes larval parasitoids. We expect this because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (fig. \ref{fig:Conceptual}). Therefore, our short-term removal of larval parasitoids has not allowed for an increase in egg parasitoid abundance after being released from intraguild predation. An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates. A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--> This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).

@@

\indent We found that the extinction of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}). For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids. Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` 
[`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`]). We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}B); however, there was no clear relationship in the original food web (table \ref{Table:Gradients}). This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on egg parasitoids section), and thus a less than additive effect on gall midges. Chamber diameter experienced positive directional selection in both food-web treatments (fig. \ref{fig:UV_Landscape}A). Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival (selection surfaces: original $\alpha_{\text{Diam}}$=

@@

`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web (original $\bar W$=

@@

`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`]).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}). This was not due to any difference between egg and larval parasitoids ($\beta_{\text{Diam}}$ contrast = 

@@

\begin{table}[h]
\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
\label{Table:Gradients}
\centering
\begin{tabular}{lcc} %c
\\ 
\hline
\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction}   \\ %& \textbf{Contrast}
\hline
$\beta_{\text{Diam}}$ & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] }& 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] }\\%& 
%\textbf{
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\

$\beta_{\text{Clutch}}$ & 
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] }\\%& 
%\textbf{
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\

$\beta_{\text{Pref}}$ &
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] }\\%&

%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] \\%&

%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\%&

%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\%& 
%\textbf{
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\%&

%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\%&

>>>>

---
# Decided to manually format the title page because I had greater control. Note that you should use put this info in the YAML header for compatability across document formats (e.g. html)
#title: Phenotypic evolution is more constrained in simpler food webs
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$ 
#- Christopher J. Greyson-Gaito$^{2,3}$ 
#- Arezoo Sootodeh$^{2}$ 
#- Brendan Locke$^{4}$ 
#- Jordi Bascompte$^{1}$ 
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

*Manuscript type*: Letter.

@@

<!-- \footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize -->

@@

The loss of biodiversity is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways. For example, in a <!--multitrophic community or -->food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection. Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities. To examine these different possibilities, we conducted a field experiment that simulated the extinction of a consumer guild associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig. \ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006]. These galls protect larva from attack by generalist predators (e.g. ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016]. We manipulated food-web structure by either excluding the guild of larval parasitoids (extinction food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (original food web, fig. \ref{fig:Conceptual}). The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system. <!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene. -->Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid. We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape. Taken together, our study gives insight to how the loss of biodiversity may constrain the evolution of interacting populations.

@@

Our analysis consisted of four parts. First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment. Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients. Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we used to measure evolutionary constraints. Finally, we used a simulation to examine how the curvature of the adaptive landscape could alter the evolvability of populations in the next generation.

@@

$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination. In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait. Similarly, any nonzero covariance terms (off-diagonal) indicate the effects of selection on additive genetic covariance between two traits. We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI. We also used this information to determine whether the curvature of each component differed between our food-web treatments.

Knowledge of the curvature matrix alone gives an incomplete picture of its indirect effect on genetic constraints. This is because genetic constraints are ultimately determined by the structure of the G-matrix, and thus may depend on its structure before selection. Although we do not know the underlying G-matrix for the traits we measured in this experiment, we can still gain insight to how our food-web treatment would alter genetic constraints. Specifically, we first calculated how our best estimate of the curvature matrix (mean values) in each treatment changed the structure of `r n_Gmats` random G-matrices. If we assume that recombination/mutation would have the same effect on gall midge populations in the original and extinction food webs, then we can estimate how the curvature matrix in the previous generation alters the G-matrix for the next generation.

The G-matrix itself is a complex structure, but recent theory has shown how its structure affects the evolvability of a population [@Hansen2008]. <!--We used evolvability as our measure of genetic constraint, as it has a solid foundation in theory of quantitative genetics and adaptive landscapes [@Hansen2008]. -->Evolvability measures the ability for a trait to evolve toward a given direction of selection, ignoring responses in every other direction [@Hansen2008]. In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can assess its evolutionary potential by computing its average evolvability over random selection gradients (here, we used `r n_random_gradients`). By computing the average evolvability for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of a population. We report the distribution of these effect sizes, rather than conduct a statistical test, because the number of replicates in a simulation can be arbitrarily high, thus making any effect size statistically significant [@White2014].

<!--
Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix. For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature matrix in each food-web treatment. This provides a conservative estimate of the factors contributing to the curvature of the adaptive landscape.

Note that our metrics of selective and genetic constraints do not put much stock in differences in the magnitude of selection between food-web treatments. This is because there is a high likelihood that we are underestimating the magnitude of selection in our treatment that excludes larval parasitoids. We expect this because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (fig. \ref{fig:Conceptual}). Therefore, our short-term removal of larval parasitoids has not allowed for an increase in egg parasitoid abundance after being released from intraguild predation. An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates. A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--><!-- This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).-->

@@

\indent We found that the extinction of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}). For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids. Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (larval parasitoids $\beta_{\text{Clutch}}$=
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` 
[`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`]). This conflicting selection is likely due to trait differences between guilds, as larger clutches may be easier targets for egg parasitoids to find, but also create a more complex gall structure that is more difficult for larval parasitoids to oviposit through.

We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}B); however, the overall magnitude of selection did not differ between treatments (table \ref{Table:Gradients}). Still, there was no clear evidence of selection on oviposition in the original food web (table \ref{Table:Gradients}). This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges. Chamber diameter experienced positive directional selection in both food-web treatments (fig. \ref{fig:UV_Landscape}A). Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival <!--(selection surfaces: original $\alpha_{\text{Diam}}$=

@@

`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`])-->
(selection surfaces: contrast $\alpha_{\text{Diam}}$=
`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` 
[`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web <!--(original $\bar W$=

@@

`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`])-->
(contrast $\bar W$=
`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean,2)` 
[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]). We expect this difference to be transient though, since egg parasitoids would increase in abundance once they are released from intraguild predation, which would make the strength of selection on gall diameter comparable to the original food web (if extinction $\bar W$=original $\bar W$, then contrast $\beta_{\text{Diam}}$=
`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$mean,2)` 
[`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]). It is worth noting that this pattern of selection is unexpected. For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is strongly correlated with another unmeasured trait that is under selection (e.g. immune response).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}). This was not due to any difference between egg and larval parasitoids ($\beta_{\text{Diam}}$ contrast = 

@@

\begin{table}[H]
\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
\label{Table:Gradients}
\centering
\begin{tabular}{lccc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction} & \textbf{Contrast} \\
\hline
$\beta_{\text{Diam}}$ & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\

$\beta_{\text{Clutch}}$ & 
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] } & 
\textbf{
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\

$\beta_{\text{Pref}}$ &
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] } &

`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &

`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &

`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
\textbf{
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &

`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\

@@

`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
